The contribution of blowing snow to cloud properties and the atmospheric radiative budget over Antarctica

### 2020-10-15 manuscript/manuscript.tex
WIP: Add results to manuscript

\textbf{Potential subtitle here}

@@

>>>>

\textbf{Influence of blowing snow on the vertical atmospheric structure}

Explicitly modelling blowing in snow in MAR leads to a notable change in the atmospheric structure of the lowermost 100s of meters above ground (Fig.\ref{fig:Test} A-C). Over the flat interior of the Antarctic Ice Sheet, the first few 100 m show a strong decrease in atmospheric temperature, with a mean 0-500 m difference of \textbf{XX $\pm$ XX \textdegree C} in elevations greater than 2000 m above mean sea level (Fig.\ref{fig:Test} A). This cooling of the near-surface atmosphere in our MAR blowing snow simulations, when compared to MAR without blowing snow, is most likely due to the efficient sublimation of airborne blowing snow particles due to the dry (and cold) surroundings over the interior Antarctic plateau. Conversely, over the steep slopes and the flat, low-lying ice shelves surrounding the grounded ice, this decrease in temperature in the blowing snow simulations is less notable. The mean 0-500 m above surface difference lies at \textbf{XX pm XX \textdegree C}. The contrasting picture between the flat interior and the steeper and lower margins of Antarctica is likely due to two effects: I) Due to the on average lower relative humidity and the greater water vapour gradients, the airborne blowing snow particles are more readily sublimated in the drier interior plateau than over the margins. This change of phase from solid to gaseous requires energy from the surrounding air to break up the bonds between the H$_2$O molecules (\textbf{CITE CC}), leading to a drop in temperature. II) Due to strong adiabatic mixing and turbulence in areas where the gravitational pull accelerates the katabatic winds over steep terrain, the snow particles are not confined to the very stable boundary layer anymore. Therefore, the sublimational cooling is less concentrated and subsequently also lower in magnitude over the margins of Antarctica and the ice shelves.

@@

\begin{figure}[H]
	\includegraphics[scale=0.7,center]{microphysics.png}
	\caption{\textbf{Difference in cloud properties between MAR with and without blowing snow.} A) Difference in cloud cover (\%) between the two MAR simulations. Red colors indicate a greater cloud cover percentage in MAR with active blowing snow parameterisation. B) Same as A) but for the difference in cloud optical depth (COD, unitless) between the two MAR simulations. C) Same as A) but for the difference in liquid water path(LWP, g/kg). D) Same as A) but for the difference in ice water path (IWP, g/kg).}
	\label{fig:micro}
\end{figure}
